%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[overlapped, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jelle Vanhorenbeke} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
% Your address
\moveleft.5\hoffset\centerline{jv.vanhorenbeke@gmail.com}
\moveleft.5\hoffset\centerline{San Francisco, CA 94110} 
\moveleft.5\hoffset\centerline{(312) 890-7147}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
% \section{OBJECTIVE}\smallskip

% To obtain a career that will allow myself to take full advantage of my passion and experience in software engineering and development operations. 

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}\smallskip

{\sl \textbf{Senior Software Engineer - Search Team}} \hfill November 2017 - October 2018 \\
Radius Intelligence, San Francisco, CA
\begin{itemize}
\item Responsible for designing and building a custom search query language as part of the External Search API.
\item Designed and built Data ingest API microservice.
\item Introduced continuous delivery to the shared code modules.
\item Architected new microservice in Kotlin to handle API callbacks.
\end{itemize} 

{\sl \textbf{Senior Software Engineer - Predictive Team}} \hfill May 2017 - November 2017 \\
Radius Intelligence, San Francisco, CA
\begin{itemize}
\item Member of Predictive team responsible for generating ML / AI models for predictive marketing.
\item Analyzed Random Forest outputs using Spark Scala and served optimum predictions to the application.
\item Owner of Job Server microservice between Predictive Jobs (model generation) and Radius Application (consumer).
\end{itemize} 

{\sl \textbf{Software Engineer - Integrations Team}} \hfill January 2016 - April 2017 \\
Radius Intelligence, San Francisco, CA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Member of Integrations team responsible for building the core Radius application in Java and Jersey.
\item Led development of Radius’s MAT integration (Eloqua) by architecting, implementing, and testing the integration.
\item Built and maintained other integrations with CRMs and MATs (Salesforce, Marketo, Facebook).
\item Designed and implemented several customer requested, highly visible application features such as Scheduled Deployments.
\end{itemize}
 
{\sl \textbf{Software Engineer (Liferay Consultant)}} \hfill January 2015 - January 2016 \\
Nintendo Of America, Chicago, IL

{\sl \textbf{Junior Software Engineer}} \hfill August 2013 - January 2015 \\
Liferay, Chicago, IL

{\sl \textbf{Full Stack Developer}} \hfill August 2011 - August 2012 \\
Vodafone Group, Madrid, Spain

%----------------------------------------------------------------------------------------
%	EDUCATION EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EDUCATION}\smallskip

{\sl Master in Information Technology and Management} \hfill 2013 \\
Illinois Institute of Technology

{\sl Bachelor in Computer Science/Engineering} \hfill 2012 \\
Technical University of Madrid

\end{resume}
\end{document}