%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[overlapped, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[margin=0.5in,]{geometry}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

% Increase text height
\textheight=700pt

\newsectionwidth{0.2in}

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
% \name{Jelle Vanhorenbeke}

\moveleft.5\hoffset\centerline{\large\bf Jelle Vanhorenbeke} % Your name at the top
 
% Your address
\moveleft.5\hoffset\centerline{jelle.jdc@gmail.com | (872) 588-0294}
% \moveleft.5\hoffset\centerline{San Francisco, CA 94118} 

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

% \address{Address 1 line 1\\Address 1 line 2\\Address 1 line 3}
% \address{Address 2 line 1\\Address 2 line 2\\Address 2 line 3}
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}

% %----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
% \section{OBJECTIVE}\smallskip

% To obtain a career that will allow myself to take full advantage of my passion and experience in software engineering and development operations. 

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}\smallskip 

%-------------------------------------------------------------------------------
% Modify the format of each position
% \begin{format}
% \title{l}\dates{r}\\
% \employer{l}\location{r}\\
% \body\\
% \end{format}
%-------------------------------------------------------------------------------

% \employer{Ask Jarvis}
% \location{San Francisco, CA}
% \dates{November 2018 - Present}
% \title{\textbf{Co-Founder | Software Engineer}}
% \begin{position}
% \end{position}

{\sl \textbf{Co-Founder | Software Engineer}} \hfill November 2018 - Present \\
Ask Jarvis, San Francisco, CA

{\sl \textbf{Senior Software Engineer | Search Team}} \hfill November 2017 - October 2018 \\
Radius Intelligence, San Francisco, CA
\begin{itemize}
\item Responsible for designing and building a custom search query language as part of the External Search API.
\item Designed and built Data ingest API microservice.
\item Introduced continuous delivery to the shared code modules.
\item Architected new microservice in Kotlin to handle API callbacks.
\end{itemize} 

{\sl \textbf{Senior Software Engineer | Predictive Team}} \hfill May 2017 - November 2017 \\
Radius Intelligence, San Francisco, CA
\begin{itemize}
\item Member of Predictive team responsible for generating ML / AI models for predictive marketing.
\item Analyzed Random Forest outputs using Spark Scala and served optimum predictions to the application.
\item Owner of Job Server microservice between Predictive Jobs (model generation) and Radius Application (consumer).
\end{itemize} 

{\sl \textbf{Software Engineer | Integrations Team}} \hfill January 2016 - April 2017 \\
Radius Intelligence, San Francisco, CA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Member of Integrations team responsible for building the core Radius application in Java and Jersey.
\item Led development of Radius’s MAT integration (Eloqua) by architecting, implementing, and testing the integration.
\item Built and maintained other integrations with CRMs and MATs (Salesforce, Marketo, Facebook).
\item Collaborated with frontend team by designing UI / UX interactions and flows in React Javascript.
\item Designed and implemented several customer requested, highly visible application features such as Scheduled Deployments.
\item Led the backend design and development of the Twitter integration.
\end{itemize}
 
{\sl \textbf{Software Engineer}} \hfill January 2015 - January 2016 \\
Nintendo Of America, Chicago, IL
\begin{itemize} 
\item Member of Nintendo’s engineering team responsible for creating a developer platform based on Liferay Portal.
\item Owned and delivered the TestRail and Liferay integration in 6 months.
\item Implemented a RESTful API with Liferay for integration with TestRail services.
\item Designed and developed the integration wizard frontend using JavaScript (jQuery) and SASS.
\item Created a web based UI test harness to analyze response times and messages.
\end{itemize} 

{\sl \textbf{Junior Software Engineer}} \hfill August 2013 - January 2015 \\
Liferay, Chicago, IL
\begin{itemize} 
\item Designed, developed, and tested an external-facing web portal during a 7-month project.
\item Architected new development environment to improve builds and remote deploys using Apache ANT scripts, Ivy for dependencies, and Jenkins for Continuous Integration.
\item Integrated the Jenkins Continuous Integration(CI) systems into the existing deployment processes.
\item Designed and implemented a strategy to migrate the client’s data and standards to Liferay custom entities.
\end{itemize} 

{\sl \textbf{Full Stack Engineer}} \hfill August 2011 - August 2012 \\
Vodafone Group, Madrid, Spain
\begin{itemize} 
\item Part of Vodafone’s online store for business team responsible for maintaining the application.
\item Designed automation systems in the content manager using C\# and .NET.
\item Created SQL procedures in SQL Server to generate new reports for the business department.
\item Implemented end-to-end application security in conjunction with an external security audit firm.
\end{itemize} 

%----------------------------------------------------------------------------------------
%	EDUCATION EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EDUCATION}\smallskip

{\sl Master in Information Technology and Management} \hfill 2013 \\
Illinois Institute of Technology
\begin{itemize}
\item Awarded a merit-based International Partnership half tuition scholarship.
\end{itemize} 

{\sl Bachelor in Computer Science/Engineering} \hfill 2012 \\
Technical University of Madrid
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Top CS program in Spain and Europe, highest honors in multiple courses.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{ACTIVITIES}\smallskip
% {\hrule width\resumewidth height 1pt}\smallskip

Golden Gate Triathlon Club, {\sl Board Member} \hfill November 2018 - Present\\
Golden Gate Triathlon Club, {\sl Ambassador Team} \hfill January 2017 - October 2018\\
Hackbright Academy, {\sl Mentor} \hfill July 2016 - January 2017\\
Ultramarathon, {\sl finisher} \hfill December 2016 \\

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY SKILLS}\smallskip

{\sl Programming Languages:} Java, Kotlin, JavaScript, Scala, C\#, SQL \\
{\sl Other Technologies:} Spring framework, PostgreSQL, MySQL, Spark, React-Native \\
 
%----------------------------------------------------------------------------------------

\end{resume}
\end{document}